Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-10-24 paper/lncsFormat.tex
finish sec 2.2; 5623 words (related works)

Knowledge base can be a good supplementary for event detection on microblog stream.
Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
For example, the microblog message ``Possible Ft. Hood Attack Thwarted (2011-07-28)'' is short, but still comprehensible because the words ``\textit{Ft. Hood}" is included in the wiki page ``\textit{Ft. Hood}", and belongs to the category ``\textit{Military}''.
By reading these two wiki pages, the model easily understands the example tweet is talking about something related to \textit{Military}.
In other words, knowledge base enriches the linkages between words, and provides more comprehensive context for microblogs.
Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
%拆成两个小图，中间说明这是transfer learning过后的
\begin{figure}[h]
        \centering
        \includegraphics[width=1.0\columnwidth]{img/hood.pdf}
        %\caption{Hood\footnote{\url{https://en.wikipedia.org/wiki/Naser_Jason_Abdo#Arrest}}\footnote{\url{https://en.wikipedia.org/wiki/Fort_Hood#2011_attack_plot}}}
        \label{fig:hood}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=.82\columnwidth]{img/NSDetectorExample.pdf}
    \caption{\textsc{LTDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example. \textsc{LTDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events.}
    \label{fig:modelDesc}
\end{figure}

@@

\textbf{Knowledge Base} The existing RDF model\cite{klyne2006rdf} lacks an efficient quick mechanism to transfer the knowledge, since it's mainly designed for managing knowledge as tuples on graph. And the query on large graph is also very expensive\cite{huang2011scalable}, which is not suitable for the scene of quickly and accurately detecting events.

@@

\newpage
\bibliographystyle{named}
\small
\bibliography{paperbib}

>>>>

Knowledge base can be a good supplementary for event detection on microblog stream.
Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
For example, the microblog message ``Possible Ft. Hood Attack Thwarted (2011-07-28)'' is short, but still comprehensible because the words ``\textit{Ft. Hood}" is included in the wiki page ``\textit{Ft. Hood}", and belongs to the category ``\textit{Military}''.
By reading these two wiki pages, the model easily understands the example tweet is talking about something related to \textit{Military}.
In other words, knowledge base enriches the linkages between words, and provides more comprehensive context for microblogs.
Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
%拆成两个小图，中间说明这是transfer learning过后的
\intextsep=3pt plus 3pt minus 1pt
\begin{figure}[h]
        \centering
        \includegraphics[width=1.0\columnwidth]{img/hood.pdf}
        %\caption{Hood\footnote{\url{https://en.wikipedia.org/wiki/Naser_Jason_Abdo#Arrest}}\footnote{\url{https://en.wikipedia.org/wiki/Fort_Hood#2011_attack_plot}}}
        \label{fig:hood}
\end{figure}

@@

\intextsep=5pt plus 3pt minus 1pt
\begin{figure}[h]
	\setlength{\abovecaptionskip}{0.cm}
	\setlength{\belowcaptionskip}{0.cm}
    \centering
    \includegraphics[width=.82\columnwidth]{img/NSDetectorExample.pdf}
    \intextsep=0pt plus 3pt minus 1pt
    \caption{\textsc{LTDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example. \textsc{LTDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events.}
    \label{fig:modelDesc}
\end{figure}

@@

\textbf{Knowledge Base} Recently, many general knowledge bases and customized knowledge bases are constructed and utilized for different text mining tasks. 
For example, Probase\cite{wu2012probase} constructs a large general probabilistic \textit{IsA} taxomomy from webpages, and is used for semantic web search, and text classification\cite{wang2014concept}.
Such kind efforts are also made by DBPedia\cite{auer2007dbpedia}, Yago\cite{fabian2007yago}, and Freebase\cite{bollacker2008freebase}. 
These works manages knowledge as tuples on graph. 
However the query on large graph is very expensive\cite{huang2011scalable}, which is not very suitable for the scene of quickly and accurately detecting events.

The customized knowledge bases such as EVIN\cite{kuzey2014evin}, Event Registry\cite{leban2014eventRegistry}, and Storybase\cite{wu2015storybase}, are designed for managing events.
These knowledge bases are mainly built on news articles.
EVIN maps the existing event-related news articles into semantic classes. 
Event Registry collects the articles by the API of News Feed Service\cite{trampuvs2012newsfeed}, then detects events, and provides the structural information of the events, such as the related Wikipedia article, timestamp, and location etc. 
Storybase introduces Wikipedia current events\footnote{\url{https://en.wikipedia.org/wiki/Portal:Current_events}} as the resources for constructing event-and-storyline knowledge base on news articles, which are provided by GDELT project\cite{leetaru2013gdelt}.
As the news articles may lag behind the microblogs when the emergency of events, it's not enough to detect events from microblog stream by directly applying these customized knowledge bases.

%近年来，知识图谱也被广泛应用在了文本挖掘领域，TKDE的文章利用wikipedia将

@@

\newpage
\bibliographystyle{aaai}
\small
\bibliography{paperbib}
